Resolving the measurement uncertainty paradox in ecological management

### 2018-11-22 manuscripts/manuscript.Rmd
fix typo

@Gordon1954 and @Schaefer1954 independently showed that the maximum sustainable yield is achieved by reducing the stock to the population to the size at which it obtains the maximum growth rate.  This stock size is known as Biomass at Maximum Sustainable Yield, $B_{MSY}$. For the Gordon-Schaefer model (and many others), this is achieved at $B_{MSY} = K/2$.  They observed that fishing at a *constant yield* (that is, an individual fish mortality, $F$, such that harvest $H = F \cdot B$) of $F_{MSY} := \tfrac{H_{MSY}}{B_{MSY}}$)  will eventually lead to a population that converges to the biomass $B_{MSY}$ and produces the maximum sustainable harvest, $H_{MSY} = r K / 4$ in this model.  From here, theory and practice diverge.

>>>>

@Gordon1954 and @Schaefer1954 independently showed that the maximum sustainable yield is achieved by reducing the stock to the population to the size at which it obtains the maximum growth rate.  This stock size is known as Biomass at Maximum Sustainable Yield, $B_{MSY}$. For the Gordon-Schaefer model (and many others), this is achieved at $B_{MSY} = K/2$.  They observed that fishing at a *constant yield* (that is, an individual fish mortality, $F$, such that harvest is biomass times mortality, $H = F \cdot B$, and thus $F_{MSY} := \tfrac{H_{MSY}}{B_{MSY}}$)  will eventually lead to a population that converges to the biomass $B_{MSY}$ and produces the maximum sustainable harvest, $H_{MSY} = r K / 4$ in this model.  From here, theory and practice diverge.

### 2018-11-22 manuscripts/manuscript.tex
fix typo

Gordon and Press (1954) and Schaefer (1954) independently showed that
the maximum sustainable yield is achieved by reducing the stock to the
population to the size at which it obtains the maximum growth rate. This
stock size is known as Biomass at Maximum Sustainable Yield,
\(B_{MSY}\). For the Gordon-Schaefer model (and many others), this is
achieved at \(B_{MSY} = K/2\). They observed that fishing at a
\emph{constant yield} (that is, an individual fish mortality, \(F\),
such that harvest \(H = F \cdot B\)) of
\(F_{MSY} := \tfrac{H_{MSY}}{B_{MSY}}\)) will eventually lead to a
population that converges to the biomass \(B_{MSY}\) and produces the
maximum sustainable harvest, \(H_{MSY} = r K / 4\) in this model. From
here, theory and practice diverge.

>>>>

Gordon and Press (1954) and Schaefer (1954) independently showed that
the maximum sustainable yield is achieved by reducing the stock to the
population to the size at which it obtains the maximum growth rate. This
stock size is known as Biomass at Maximum Sustainable Yield,
\(B_{MSY}\). For the Gordon-Schaefer model (and many others), this is
achieved at \(B_{MSY} = K/2\). They observed that fishing at a
\emph{constant yield} (that is, an individual fish mortality, \(F\),
such that harvest is biomass times mortality, \(H = F \cdot B\), and
thus \(F_{MSY} := \tfrac{H_{MSY}}{B_{MSY}}\)) will eventually lead to a
population that converges to the biomass \(B_{MSY}\) and produces the
maximum sustainable harvest, \(H_{MSY} = r K / 4\) in this model. From
here, theory and practice diverge.
